### 2021-01-23 chatbot_classification/acl_2021/experiments.tex
upload paper in acl_2021 format

\begin{enumerate}
  \item \emph{ITG},  is  a proprietory FAQ dataset from real-world
  chatbot  project,  which is composed of question and answer pairs about online
  English teaching. It contains 3,938 sample questions for 228 class labels, and
  each class label corresponds to a unique answer.

@@

  \item \emph{BANKING77}, is a intention detection dataset for bank
  customer  services.  The  raw dataset contains 13,084 data points for 77 class
  labels \cite{casanueva2020efficient}.
\end{enumerate}

Regarding  the first two datasets, we conduct 3-fold cross validation experiments
that   70   percent   as  training,  15  percent  as  validation  and  testing
respectively,  and  report  the  averaged  testing results. Regarding the last
three datasets, we conduct experiments using a sampling method similar to that
in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
settings.  We  fix  a  test  data for each one, and examine their performances
using  5,  10,  15,  20,  30,  and 50 samples per class label respectively for
training.  This  is important, as in practice, a task-specific chatbot usually
starts  with  merely  a  handful of labeled data available in the early stage.
Besides,  in  the  active  learning framework, building an effective auxiliary
system  with limited resource is also quite important to help developers label
data more efficiently.

\subsection{Baselines}
We choose three kinds of system to construct our baselines. All our pretrained 
model baselines are being fine-tuned on all the experimental datasets. Additionally, 
the similarity model baseline will use the same fine-tuning process on Quora dataset  \cite{iyer2017first} as all our SFC models. As our researched problem is the application without sufficient data, the similarity model baseline is influenced due to insufficient in-domain data to a great extent. Thus, generally the similarity model baseline has to use external data.

@@

  \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
  RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
  RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
  models  in  the  short  text  classification  task  in  our  experiments. In
  inference,  we  use  an  elastic search to find a set of potential candidate
  labels for the similarity model, to guarantee a reasonable running time.
\end{enumerate}

Our SFC systems include two-stage SFC with ablation, trained with two tasks
separately and both, and joint SFC with all three tasks.

\subsection{Implementation Details}
For  our  SFC  systems,  we  use RoBERTa-large as the pretrained model for both
classification  task  and  sentence-pair similarity task. We fine-tune
our  SFC  system  on  our datasets with max sequence length of 128,
learning  rate  of 1.5e-5 for RoBERTa-large pretrained model and learning rate
of  5e-4  for  task-specific  layer  with polynomial decay and Adam optimizer.

In two-stage SFC, in equ. \ref{eq:two-stage_SFC_loss} the weights of two tasks
are  set  as  $\alpha_S=0.125$ and $\alpha_K=0.875$ in our setting. The reason
for  giving  task  2 relatively more weights is that according to the ablation
experiments  we  did  in Section \ref{sec:exp}, task 2 contributes more to the
overall  performance.  In  joint  SFC,  in  equ.  \ref{eq:joint_SFC_loss}, the
weights  of  three  tasks  are  set  as  $\alpha_S=0.25$,  $\alpha_K=0.25$ and
$\alpha_C=0.5$  in  our setting. Overall, the task weights are less sensitive
in Joint SFC than in two-stage SFC.

For  the  experiments  in  Table  \ref{tbe:table2},  we  empirically  set  the
hyperparameter  to  be  $K=5$  and  $P=10$  for  all  SFC  variants.  In Table
\ref{tbe:table3},  we  conduct extensive experiments to see the performance of
SFC system under various hyperparameter settings.

As for the training time, in our settings, our joint SFC model needs about 14
hours to reach convergence using a single Nvidia RTX8000 GPU. In comparison, the classification baseline model needs about 5 hours and the similarity baseline model
needs about 12 hours, which indicates that our joint SFC model spends less training
time than the summation of two baseline models due to faster convergence.

As for the inference time, the classification model baseline is about 0.2 ms;
the similarity model baseline is about 0.5 ms and our joint SFC model takes only 0.6 ms.
Actually both the similarity model baseline and our joint SFC can be GPU
parallelized in the similarity computation, if we need pretty fast response time
in a real product.

@@

%The performance of each model is measured in F1 score on the fixed
%test  set  for  each  dataset.  
%Overall,  two-stage  SFC systems in multi-task training deliver  moderate 
%improvements  over  corresponding baselines, and joint SFC deliver more
%significant and consistent improvements over the best baseline, RoBERTa based
%classification. In following content, we dive into more details.

@@

@@

\subsubsection*{Is  the  fusion of classification and similarity models
helpful?}  We  compare  joint SFC with classification and similarity based
baselines respectively.

@@

    \begin{tabular}{|c|c|c|c|c|c|c|}
      \hline 
      \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
      \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
      \hline
      \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
      \cline{2-7}
      \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
      \hline
      \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
      \cline{2-7}
      \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
      \hline
    \end{tabular}
    \par
  \end{centering}
  \caption{
    We  show the performances of SFC from different settings of
    hyperparameters, $K$  denoting the candidate class number from stage 1,
    $P$ denoting the number of sampled sententence pair in stage 2. 
  }
  \label{tbe:table3}
\end{table*}

Regarding the  classification  models,  joint SFC
outperforms RoBERTa-large based, the strongest among all baselines, 
by 2.04 percent points on average F1 score over 5 datasets.  
Especially, ALBERT.xxlarge based is rather unstable  in this senario. Thus, 
we did multiple run with different settings and  report the  best  ones here. 
Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
n almost all experiment settings.

@@

The above analysis illustrates that suitable fusing the two kinds of models
can take their advantages.

@@

The joint training does not improve the classification performance in stage 1,
measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
candidate  class  labels, which can further improve the effect of sentence pair
similarity training. The reason is that, a classification model
inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
pair similairity model in the joint SFC poses more positive effect in optimizing the 
candidate labels.

@@

\subsubsection*{Settings  of  hyperparameters} 
In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
roughly obatin five combinations of hyperparameters.

We find  that the best setting of hyperparameters is different from datasets
of  different  data  size.  The  class label number of ITG and Amazon-670k are
similar  in  our  experimental setting, which is around 250. However the total
amount of data points of ITG is approximately 2 times larger than Amazon-670k.
Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
candidate  classes to sample enough effective sentence pairs for sentence-pair
model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
good choice.

However,  in  spite of the effect on evaluation performance brought by different
settings  of hyperparameters, joint SFC still steadily outperforms two-stage SFC
by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
datasets.

>>>>

\begin{enumerate}
  \item \emph{ITG},  is  a proprietary FAQ dataset from real-world
  chatbot  project,  which is composed of question and answer pairs about online
  English teaching. It contains 3,938 sample questions for 228 class labels, and
  each class label corresponds to a unique answer.

@@

  \item \emph{BANKING77}, is a intention detection dataset for bank
  customer  services.  The  raw dataset contains 13,084 data points for 77 class
  labels \cite{casanueva2020efficient}.

  \item \emph{FRAMES}, is a collection of multi-domain dialogues dealing with
hotel bookings. The raw data is consists of 1369 human-human
dialogues with slot filling information. There are 30,522 utterances in total for 21 intents and 49 slots \cite{asri2017frames}.

  \item \emph{ATIS}, is a popular dataset for intent detection of flight reservations with slot filling\cite{tur2010left}. The raw data's training, development and test sets contain 4,478, 500 and 893 utterances, respectively. There are 120 slot labels and 21 intent types for the training set.

\end{enumerate}

Regarding  the first two datasets, we conduct 3-fold cross validation experiments
that   70   percent   as  training,  15  percent  as  validation  and  testing
respectively,  and  report  the  averaged  testing results. Regarding the last
five datasets, we conduct experiments using a sampling method similar to that
in   \cite{casanueva2020efficient}   yet  in  a  more  sophisticated  few-shot
settings.  We  fix  a  test  data for each one, and examine their performances
using  5,  10,  15,  20,  30,  or 50 samples per class label respectively for
training.  This  is important, as in practice, a task-specific chatbot usually
starts  with  merely  a  handful of labeled data available in the early stage.
Besides,  in  the  active  learning framework, building an effective auxiliary
system  with limited resource is also quite important to help developers label
data more efficiently.

\subsection{Baselines}
We  choose  three kinds of system as our baselines. All our pretrained
model   baselines  are  fine-tuned  on  our datasets.
Especially, the similarity  model  baseline  and all similarity modules in SFCs
use extra Quora  dataset  \cite{iyer2017first}  to enhance system performance.

@@

  \item   \emph{Pre-trained   model   based   similarity   model}.  We  choose
  RoBERTa-large  as  our  fundamental  module as our SFC systems are based on
  RoBERTa  too, and RoBERTa is empirically more effective than other pretrained
  models  in  the  short  text  classification  task  in  our  experiments. In
  inference,  we  use  an  elastic search to find a set of potential candidate
  labels for the similarity model, to guarantee a reasonable running time.

  \item \emph{Pre-trained model based text classification and NER joint model}. Considering  a  joint  model,  our  SFC framework  is also supportive of NER task. That  is  in  stage  1,  based on the  output  states from a
pretrained model, we can derive a fourth task for NER loss. For performance comparison, we choose the state-of-the-art model, which is RoBERTa-large with NER loss, using the same model structure with \cite{chen2019bert}, as our baseline.
\end{enumerate}

Our SFC systems include two-stage SFC with ablation, trained with two tasks
separately and both, and joint SFC with all three tasks. All setting details can
be found in the appendix due to the space limitation.

@@

@@

\begin{table}
  \begin{centering}
    \scalebox{0.58}{
      \begin{tabular}{|c|ccc|ccc|}
        \hline
        \multicolumn{1}{|c|}{\multirow{2}*{\textbf{Models}} }& \multicolumn{3}{c|}{\textbf{FRAMES}}& \multicolumn{3}{c|}{\textbf{ATIS}}\tabularnewline
        \cline{2-7}
        \multicolumn{1}{|c|}{} & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$
        & $\textbf{10}$ & $\textbf{20}$ & $\textbf{50}$\tabularnewline
        \hline
        RoBERTa-large & \multirow{2}*{${0.3456}$} &
        \multirow{2}*{${0.4043}$} & \multirow{2}*{${0.4262}$} &
        \multirow{2}*{${0.9349}$} & \multirow{2}*{${0.9757}$} & 
        \multirow{2}*{${0.9800}$}\tabularnewline
        (classification) & & & & & & \tabularnewline
        \hline
        RoBERTa-large & \multirow{2}*{${0.3520}$} &
        \multirow{2}*{${0.4088}$} & \multirow{2}*{${0.4353}$} &
        \multirow{2}*{${0.9560}$} & \multirow{2}*{${0.9706}$} & 
        \multirow{2}*{${0.9832}$}\tabularnewline
        (classification w/ NER) & & & & & & \tabularnewline
        \hline
        Joint SFC & \multirow{2}*{${0.3843}$} &
        \multirow{2}*{${0.4130}$} & \multirow{2}*{${0.4390}$} &
        \multirow{2}*{${0.9404}$} & \multirow{2}*{${0.9761}$} & 
        \multirow{2}*{${0.9825}$}\tabularnewline
        (w/o NER) & & & & & & \tabularnewline
        \hline
        Joint SFC & \multirow{2}*{$\textbf{0.3925}$} &
        \multirow{2}*{$\textbf{0.4420}$} & \multirow{2}*{$\textbf{0.4456}$} &
        \multirow{2}*{${0.9442}$} & \multirow{2}*{${0.9729}$} & 
        \multirow{2}*{${0.9826}$}\tabularnewline
        (w/ NER) & & & & & & \tabularnewline
        \hline
      \end{tabular}
    }

  \end{centering}
  \caption{F1 scores on two task-specific datasets for joint training of sentence classification and NER in chatbot domain under low resource. For both FRAMES and ATIS, we set up various few-shot settings(10/20/50 samples per intent) while keeping the original test set.}
  \label{tbe:addtional ner experiments}
\end{table}

@@

\subsubsection*{Is  the  fusion of classification and similarity models
helpful?}  We  compare  joint SFC with classification, similarity and NER joint model based baselines respectively.

@@

    \begin{tabular}{|c|c|c|c|c|c|c|}
      \hline 
      \multicolumn{1}{|c|}{\multirow{2}*{Dataset}}&\multicolumn{1}{c|}{\multirow{2}*{Model}}& $K=3$ & $K=5$ & $K=10$ & $K=15$ & $K=20$\tabularnewline
      \multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & $P=20$ & $P=10$ & $P=5$ & $P=4$ & $P=3$\tabularnewline
      \hline
      \multicolumn{1}{|c|}{\multirow{2}*{ITG}}& two-stage SFC & $0.8034$ & $0.8124$ & $0.8008$ & $0.7967$ & $0.7934$\tabularnewline
      \cline{2-7}
      \multicolumn{1}{|c|}{} & joint SFC & $0.7986$ & $0.8114$ & $0.8010$ & $0.7972$ & $0.7918$\tabularnewline
      \hline
      \multicolumn{1}{|c|}{\multirow{2}*{Amazon-670k}}& two-stage SFC & $0.7278$ & $0.7364$ & $0.7366$ & $0.7328$ & $0.7204$\tabularnewline
      \cline{2-7}
      \multicolumn{1}{|c|}{} & joint SFC & $0.7334$ & $0.7445$ & $0.7516$ & $0.7344$ & $0.7373$\tabularnewline
      \hline
    \end{tabular}
    \par
  \end{centering}
  \caption{
    We  show the performances of SFC from different settings of
    hyperparameters, $K$  denoting the candidate class number from stage 1,
    $P$ denoting the number of sampled sentence pair in stage 2. 
  }
  \label{tbe:table3}
\end{table*}

Regarding the  classification  models,  joint SFC
outperforms RoBERTa-large based, the strongest among all baselines, 
by 2.04 percent points on average F1 score over 5 datasets.  
Especially, ALBERT.xxlarge based is rather unstable  in this scenario. Thus, 
we did multiple run with different settings and  report the  best  ones here. 
Comparatively,  RoBERTa  based is  the  most stable and has the best performance 
n almost all experiment settings.

@@

As for the intent classification and NER joint model, we choose the state-of-the-art RoBERTa-large model with NER loss as our baseline. For ablation study, we did experiments on Joint SFC model with and without NER loss respectively. Our Joint SFC without NER loss still outperforms RoBERTa with NER loss baseline by 1.34 percent points on average. This indicates that the fusion of classification and similarity can even works better than utilizing additional NER information under few-shot chatbot scenario. Moreover, our Joint SFC with NER loss achieves further improvement by 2.80 percent points over RoBERTa with NER loss baseline. In this way, we show the compatibility of our Joint SFC model with extra semantic information.

The above analysis illustrates that suitable fusing these two kinds of models
can take their advantages.

@@

The joint training does not improve the classification performance in stage 1,
measured  by  top-1  accuracy.  However,  it  improves  the  quality of top-5
candidate  class  labels, which can further improve the effect of sentence pair
similarity training. The reason is that, a classification model
inherently optimizes the objective loss, 0-1 error of top-1 here; the sentence
pair similarity model in the joint SFC poses more positive effect in optimizing the 
candidate labels.

@@

### 2021-01-23 chatbot_classification/acl_2021/methodology.tex
upload paper in acl_2021 format

\begin{table*}
  \begin{centering}
    \scalebox{0.75}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
        \hline 
        HWU64 & intention detection & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & intention detection & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & intention detection & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{Statistics for all datasets and few shot settings.}

@@

    F1 scores  on  five  task-specific  datasets text classification in chatbot

>>>>

\begin{table*}
  \begin{centering}
    \scalebox{0.75}{
      \begin{tabular}{|c|c|c|c|c|c|}
        \hline 
        \textbf{Dataset} & \textbf{Domain} & \textbf{\#Class} &
        \textbf{\#Training Samples} & \textbf{\#Samples/Class} & \textbf{Settings}\tabularnewline
        \hline 
        ITG & FAQ chatbot & 228 & 3938 * 0.7 & 12 & 3-fold\tabularnewline
        \hline 
        Amazon-670k & Product review & 250 & 2658 * 0.7 & 8 & 3-fold\tabularnewline
        \hline 
        HWU64 & intent detect & 64 & [320, 640, 960, 1280, 1920, 3200] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        CLINC150 & intent detect & 150 & [750, 1500, 2250, 3000, 4500, 7500] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        BANKING77 & intent detect & 77 & [385, 770, 1155, 1540, 2310, 3850] & [5, 10, 15, 20, 30, 50] & data sampling\tabularnewline
        \hline 
        FRAMES & intent detect with ner & 21 & [208, 408, 984] & [10, 20, 50] & data sampling\tabularnewline
        \hline
        ATIS & inent detect with ner & 21 & [168, 303, 544] & [10, 20, 50] & data sampling\tabularnewline
        \hline
      \end{tabular}
    }
    \par
  \end{centering}
  \caption{Statistics for all datasets and few shot settings.}

@@

    F1 scores  on  five  task-specific  datasets for text classification in chatbot
